### 2016-05-29 R/ITHIM.Rmd
Update to ITHIM.Rmd

```{r RRs}
RR <- createActiveTransportRRs()
RR.baseline <- lapply(RR, MET2RR, ITHIM.baseline$quintiles$TotalMET)
RR.scenario <- lapply(RR, MET2RR, ITHIM.scenario$quintiles$TotalMET)

diseaseBurden.scenario <- mapply(ratioForList,RR.baseline, RR.scenario, SIMPLIFY = FALSE)
diseaseBurden.baseline <- mapply(ratioForList,RR.baseline, RR.baseline, SIMPLIFY = FALSE) # What!
AF <- mapply(AFForList, diseaseBurden.scenario,diseaseBurden.baseline, SIMPLIFY = FALSE)
```

@@

```{r AF}
100*round(AF$BreastCancer[-(1:2),],4)

```{r explore}
names(ITHIM.baseline$parameters)
```

We use Rws to estimate mean walking speed and from that mean walking
METs.  Mean cycling METs, however, is constant and is not a function
of mean cycling speed or Rcs.  So, I do not think Rcs is currently
used.

To see the help page for a function use help().
```{r help, eval = FALSE}
help(createParameterList)
help(computeMeansMatrices)
help(getQuintiles)
```

@@

```{r plot1, echo = FALSE}
D <- melt(ITHIM$means$meanActiveTransportTime, c("age","sex"), value.name = "activeTransportTime")
p <- ggplot(D, aes(age,  activeTransportTime)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

```{r plot2, echo = FALSE}
D <- melt(ITHIM$parameters$Rwt, c("age","sex"), value.name = "rhowt")
p <- ggplot(D, aes(age,  rhowt)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

# Code Graveyard

### Active Transport Estimates (Speed and Distance by Transport Mode)
These data were ripped out of the EXCEL workbook and vary per scenario.
```{r transportData, eval = FALSE, echo = FALSE}

>>>>

```{r RRs}
comparitiveRisk <- compareModels(ITHIM.baseline,ITHIM.scenario)
names(comparitiveRisk)
```

```{r show}
100*round(comparitiveRisk$AF$BreastCancer,4)
```

@@

```{r AF, echo = FALSE}
lapply(comparitiveRisk$AF[-(which(names(comparitiveRisk$AF)%in%c("CVD","Diabetes")))], function(x) 100*round(x[-(1:2),],4))
```
### Relative Risk Model
```{r explore}
names(ITHIM.baseline$parameters)
```
```{r RRFigure, echo = FALSE}
phi <- function(x,k=0.5,phi0=comparitiveRisk$RR.baseline$BreastCancer$F[1,1]) phi0^{x^k}
plot(x = xvec <- seq(0,xmax <- 10,length.out=1e3), y = phi(xvec, k = 0.25), main = "Relative Risk Models for MET Exposure", xlab = "METs per week", ylab = "Breast Cancer Relative Risk", type = "l", lwd = 2, col = 1, ylim = c(0.9,1),xlim=c(0,xmax))
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.375), lwd = 2, col = 3)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.5), lwd = 2, col = 2)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 1), lwd = 2, col = 4)
legend(x="topright",legend=paste0("k=",c("0.25","0.375","0.5","1")), col=1:4,lty=1,lwd=2)
```

To see the help page for a function use help().
```{r help, eval = FALSE}
help(createParameterList)
```

@@

```{r plot2, echo = FALSE, fig.width = 12}
plotRR(comparitiveRisk$RR.baseline$Depression,comparitiveRisk$RR.scenario$Depression) + coord_cartesian(ylim = c(0.75, 1.05))+ggtitle("Depression")
```

```{r plot3, echo = FALSE, fig.width = 12, eval = FALSE}
plotRR(comparitiveRisk$RR.baseline$BreastCancer,comparitiveRisk$RR.scenario$BreastCancer) + coord_cartesian(ylim = c(0.75, 1.05)) + ggtitle("Breast Cancer")
```

```{r plot4, echo = FALSE, fig.height = 12}
D<-melt(comparitiveRisk$AF)
names(D)<- c("age","sex","AF","disease")
p <- ggplot(D, aes(age,AF)) + geom_bar(aes(fill=sex), stat = "identity") + facet_grid( disease ~ .) + coord_cartesian(ylim = c(0, 0.1))
p
```
# Code Graveyard

### Active Transport Estimates (Speed and Distance by Transport Mode)
```{r plot1, echo = FALSE, eval = FALSE}
D <- melt(ITHIM.baseline$means$meanActiveTransportTime, c("age","sex"), value.name = "activeTransportTime")
p <- ggplot(D, aes(age,  activeTransportTime)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p + coord_cartesian(ylim = c(0.75, 1.05))
```

These data were ripped out of the EXCEL workbook and vary per scenario.
```{r transportData, eval = FALSE, echo = FALSE}
